Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-19 ba_resubmit/kundinger_resubmit2.tex
working on comments.

In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. 
We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.

@@

>>>>

%\textcolor{red}{In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. 
%We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.}

@@

%\textcolor{red}{In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. 
%We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.}

\textcolor{teal}{We now explain how we accomodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing completely at random (MCAR, per \cite{LittleRubin2002}). With the MCAR assumption, we can marginalize over the missing data in (\ref{eqn:likelihood}), and do all computation simply using the observed data.}

%are ignorable (or random) \citep{LittleRubin2002}. The likelihood becomes that in (\ref{eqn:likelihood}), following directly from \cite{sadinle_bayesian_2017}. Note that both assumptions used here are for computational convenience. Missing completely at random (MCAR) applies when the probability that a value of a variable is missing does not depend on the observed or unobserved variables. Missing at random (MAR) is present when the probability of missingness depends only on (the values of other) observed variables.}
%\textcolor{red}{In Sadinle (2017), he assumes MAR and in the JASA paper he assumes ignorability.}
